### 2021-06-18 docs/manuscript/manuscript.tex
State that the interval for interactions was chosen arbitrarily
Add citation to Exelby et al. 2021

The set of interaction values was represented as adjacency matrices $W \in
\mathbb{R}^{3\times4}$ where $i$ represents a regulated node of the GRN and $j$
represents a regulator node of the GRN (Fig \ref{fig:model}A and
\ref{fig:model}B) with $w_{\textit{ij}}~\in [-10,\ 10]$. Values in these
matrices can be negative, zero or positive and represent represion, no
interaction, or activation respectively. The magnitude of the value is
proportional to the strength of the interaction. In this study we define
a 'genotype' as the set of interaction, diffusion and degradation values that
represent a GRN.\\

@@

Robustness is an important feature of patterning mediated by
morphogens~\cite{lo_robust_2015}. In our study, the most abundant topologies were
found to be part of highly connected clusters in the neutral network, and this fact
indicates that these topologies are both robust to quantitative changes in the
strength of interactions and diffusion and degradation parameters as well as to
qualitative changes in the topology itself. As robustness and evolvability are
not mutually exclusive properties~\cite{wagner_robustness_2008}, it is likely
that these topologies are also evolvable.

>>>>

The set of interaction values was represented as adjacency matrices $W \in
\mathbb{R}^{3\times4}$ where $i$ represents a regulated node of the GRN and $j$
represents a regulator node of the GRN (Fig \ref{fig:model}A and
\ref{fig:model}B) with $w_{\textit{ij}}~\in [-10,\ 10]$ (this interval was arbitrarily
chosen and it is inherited from the model of Munteanu~et~al.~\cite{munteanu_2014}
and Cotterell~\&~Sharpe\cite{Cotterell2010}). Values in these
matrices can be negative, zero or positive and represent represion, no
interaction, or activation respectively. The magnitude of the value is
proportional to the strength of the interaction. In this study we define
a 'genotype' as the set of interaction, diffusion and degradation values that
represent a GRN.\\

@@

Robustness is an important feature of patterning mediated by morphogens, and
the GRNs involved can be selected in an evolutionary process not only by its final
steady state but also by its ability to buffer noise~\cite{lo_robust_2015, exelby_2021}.
In our study, the most abundant topologies were
found to be part of highly connected clusters in the neutral network, and this fact
indicates that these topologies are both robust to quantitative changes in the
strength of interactions and diffusion and degradation parameters as well as to
qualitative changes in the topology itself. As robustness and evolvability are
not mutually exclusive properties~\cite{wagner_robustness_2008}, it is likely
that these topologies are also evolvable.
